Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-19 2015-turklang-kazdep/paper.tex
werw
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60841 72bbbca6-d526-0410-a7d9-f06f51895060

\usepackage{multirow}
\usepackage[colorlinks=true,citecolor=black,linkcolor=black,urlcolor=blue]{hyperref}

@@

\abstract{250-300-word ``extended abstract in English''}

@@

@@

@@

\begin{table}
  \centering
  \begin{tabular}{|l|l|r|r|r|}
    \hline
    \textbf{Document} & \textbf{Description} & \textbf{Sentences} & \textbf{Tokens} & \textbf{Avg. length}\\
    \hline
    Declaration on Human Rights & Legal text on human rights & 25 & 409 & 16.3 \\
    Phrasebook & Phrases from Wikitravel & 37 & 205 & 5.5 \\
    Жиырма Бесінші Сөз & Philosophical text & 34 & 525 & 15.4 \\ 
    Өлген қазан & Folk tale & 8 & 140 & 17.5 \\
    Азамат қайда? & Story for children and language learners & 48 & 434 & 9.0 \\
    Футболдан әлем чемпионаты 2014  & Wikipedia article (2014 World Cup) & 14 & 246 & 17.5 \\
    Иран & Wikipedia article (Iran) & 111 & 1562 & 14.0 \\
    Радиан & Wikipedia article (Radian) & 2 & 17 & 8.5 \\
    \hline
  \end{tabular}
  \caption{Composition of the corpus. The corpus covers a range of genres and text types.}
\end{table}

@@

% tokenisation
\cite{Washington14}

@@

>>>>

\usepackage{multirow}
\usepackage[small,bf]{caption} % CHECK IF THIS IS OK
\usepackage[colorlinks=true,citecolor=black,linkcolor=black,urlcolor=blue]{hyperref}

@@

%250-300-word ``extended abstract in English''
\abstract{
This article describes the first steps towards a free/open-source dependency treebank
for Kazakh based on universal dependency (UD) annotation standards. The treebank is 
based on texts from a range of open-source and public domain sources ensuring its 
free availability and extensibility. 
}

@@

% case and function
% "zero" derivation

@@

% what are treebanks used for ?

@@

\begin{table}
  \centering
\begin{small}
  \begin{tabular}{|l|l|r|r|r|}
    \hline
    \textbf{Document} & \textbf{Description} & \textbf{Sentences} & \textbf{Tokens} & \textbf{Avg. length}\\
    \hline
    UN Declaration on Human Rights & Legal text on human rights & 25 & 409 & 16.3 \\
    Phrasebook & Phrases from Wikitravel & 37 & 205 & 5.5 \\
    Жиырма Бесінші Сөз & Philosophical text & 34 & 525 & 15.4 \\ 
    Өлген қазан & Folk tale & 8 & 140 & 17.5 \\
    Азамат қайда? & Story for language learners & 48 & 434 & 9.0 \\
    Футболдан әлем чемпионаты 2014  & Wikipedia article (2014 World Cup) & 14 & 246 & 17.5 \\
    Иран & Wikipedia article (Iran) & 111 & 1562 & 14.0 \\
    Радиан & Wikipedia article (Radian) & 2 & 17 & 8.5 \\
    \hline
    \multicolumn{2}{c|}{~} & - & - & - \\\cline{3-5}
  \end{tabular}
\end{small}
  \caption{Composition of the corpus. The corpus covers a range of genres and text types from 
    free and public-domain sources.}
\end{table}

@@

% tokenisation
% http://universaldependencies.github.io/docs/u/overview/tokenization.html
\cite{Washington14}

@@

% general procedure

% - disambiguate
% - annotate
% - check the tree structure
% - fix errors
% - check for label consistency
% - fix errors
